The imputation methods big test

### 2020-04-27 pd2.Rmd
add legend to plot

colors <- c("remove" = "orange", "median" = "cyan", "mice" = "green",
            "missForest" = "red", "VIM" = "blue")

require(scales)
ggplot(data = imputation_times, aes(x = dataset_id)) +
  geom_point(aes(y = remove), color = colors[1], size = 2, shape = 18) +
  geom_point(aes(y = median), color = colors[2], size = 2, shape = 16) +
  geom_point(aes(y = mice), color = colors[3], size = 2, shape = 15) +
  geom_point(aes(y = missForest), color = colors[4], size = 2, shape = 17) +
  geom_point(aes(y = VIM), color = colors[5], size = 2, shape = 19) +
  ggtitle("Datasets' imputations times") +
  theme_gray() +
  scale_y_continuous(trans = log2_trans(),
    breaks = trans_breaks("log2", function(x) 2^x),
    labels = trans_format("log2", math_format(2^.x))) +
  labs(x = "Dataset Id",
       y = "Imputation time [in seconds]",
       color = "Legend") +
  scale_color_manual(name = ":-)", values = colors) +
  theme(legend.position="right",
        plot.title = element_text(hjust = 0.5))
```

>>>>

colors <- c("remove" = "orange", "median" = "cyan", "mice" = "green",
            "missForest" = "red", "VIM" = "blue")
imptimes <- melt(imputation_times)

require(scales)

# żeby połączyć kolory i shape w legendzie zobacz
# https://stackoverflow.com/questions/12410908/combine-legends-for-color-and-shape-into-a-single-legend

ggplot(data=imptimes, aes(x = dataset_id, y = value, color = variable, shape = variable)) + geom_point() + 
#ggplot(data = imputation_times, aes(x = dataset_id, y )) +
  #geom_point(aes(y = remove), color = colors[1], size = 2, shape = 18) +
  #geom_point(aes(y = median), color = colors[2], size = 2, shape = 16) +
  #geom_point(aes(y = mice), color = colors[3], size = 2, shape = 15) +
  #geom_point(aes(y = missForest), color = colors[4], size = 2, shape = 17) +
  #geom_point(aes(y = VIM), color = colors[5], size = 2, shape = 19) +
  ggtitle("Datasets' imputations times") +
  theme_gray() +
  scale_y_continuous(trans = log2_trans(),
    breaks = trans_breaks("log2", function(x) 2^x),
    labels = trans_format("log2", math_format(2^.x))) +
  labs(x = "Dataset Id",
       y = "Imputation time [in seconds]",
       color = "Legend") +
  scale_color_manual(name = ":-)", values = colors) +
  theme(legend.position="right",
        plot.title = element_text(hjust = 0.5))
```
